---
title: "scRNA-seq workshop 2019"
output: html_notebook
---

# Goal
To show people how we analyze scRNA-seq

# Dependencies

```{r}
library(Seurat)
library(ggplot2)
library(dplyr)
library(tidyr)
```

# Load the data
```{r}
pbmc.data <- Read10X(data.dir ="../data/filtered_gene_bc_matrices_8kpbmc/GRCh38/")
```

```{r}
pbmc <- CreateSeuratObject(pbmc.data, min.cells = 3, project = "PBMC")
```

# Quality control

```{r}
pbmc[["percent.mito"]] <- PercentageFeatureSet(pbmc, pattern = "^MT-")

VlnPlot(pbmc, features = c("nFeature_RNA", "nCount_RNA", "percent.mito"), ncol = 3)
```

# Filtering
```{r}
pbmc <- subset(pbmc, subset = nFeature_RNA > 200 & percent.mito < 6)
```

# Normalization
```{r}
pbmc <- NormalizeData(pbmc) #uses log normalization and library size scaling
```

# Identifying most variable genes

```{r}
pbmc <- FindVariableFeatures(pbmc, selection.method = "vst",
                             nfeatures = 2000)
```

# Scale data and regress technical factors

```{r}
pbmc <- ScaleData(pbmc, vars.to.regress=c("nCount_RNA",
                                          "percent.mito"))
```

# PCA

```{r}
pbmc <- RunPCA(pbmc)
```


DimPlot()
FeaturePlot()

```{r}
DimPlot(pbmc)
FeaturePlot(pbmc, features="LYZ")
FeaturePlot(pbmc, features="percent.mito")
```

```{r}
DimPlot(pbmc, dims = c(1,3))
```

# Run UMAP

```{r}
ElbowPlot(pbmc, ndims=50)
```


```{r}
pbmc <- RunUMAP(pbmc, dims=1:30)
```

```{r}
DimPlot(pbmc)
```

```{r}
FeaturePlot(pbmc, features = c("LYZ", "CD3D"))
```

# Clustering
```{r}
pbmc <- FindNeighbors(pbmc, dims=1:30)
pbmc <- FindClusters(pbmc, resolution = 0.3)
```

```{r}
DimPlot(pbmc, label=T)
```

Clusters are stored
```{r}
head(pbmc@meta.data)

```

```{r}
table(pbmc$seurat_clusters)
```

# Find Markers of Each Cluster
Two functions in Seurat to know about
FindMarkers() - One cluster only
FindAllMarkers() - All clusters
```{r}
pbmc.markers <- FindAllMarkers(pbmc, logfc.threshold = 0.75)
```



Sample ggplot2 code
```{r}
data <- pbmc@meta.data
data$UMAP1 <- Embeddings(pbmc, 'umap')[,1]
data$UMAP2 <- Embeddings(pbmc, 'umap')[,2]

data_plot <- ggplot(data, aes(x=UMAP1, y=UMAP2)) +
  geom_point(size=0.2, alpha=0.5, aes(color=seurat_clusters)) +
  theme_classic() +
  theme(axis.text=element_text(size=12, color="black"))

data_plot
```



